---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width = 10,
  fig.retina = 3
)
```

# ggsegYan

<!-- badges: start -->
[![R-CMD-check](https://github.com/ggsegverse/ggsegYan/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ggsegverse/ggsegYan/actions/workflows/R-CMD-check.yaml)
[![r-universe](https://ggseg.r-universe.dev/badges/ggsegYan)](https://ggseg.r-universe.dev/ggsegYan)
<!-- badges: end -->

Yan 2023 homotopic cortical parcellation atlases for the ggseg ecosystem.
Includes 7-network and 17-network parcellations at resolutions from 100 to
1000 parcels.

## Installation

We recommend installing the ggseg-atlases through the ggseg
[r-universe](https://ggseg.r-universe.dev/ui#builds):

```{r}
#| label: install-r-universe
#| eval: false
options(repos = c(
  ggseg = "https://ggseg.r-universe.dev",
  CRAN = "https://cloud.r-project.org"
))

install.packages("ggsegYan")
```

You can install this package from [GitHub](https://github.com/) with:

```r
# install.packages("pak")
pak::pak("ggsegverse/ggsegYan")
```

## Yan 7-network (400 parcels)

```{r}
#| label: yan7-400
library(ggseg)
library(ggsegYan)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = yan7_400(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = yan7_400()$palette, na.value = "grey") +
  theme_void()
```

## Yan 17-network (400 parcels)

```{r}
#| label: yan17-400
ggplot() +
  geom_brain(
    atlas = yan17_400(),
    mapping = aes(fill = label),
    position = position_brain(hemi ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = yan17_400()$palette, na.value = "grey") +
  theme_void()
```

## Data source

Yan X, Kong R, Xue A, et al. (2023). Homotopic local-global parcellation
of the human cerebral cortex from resting-state functional connectivity.
*NeuroImage*, 273, 120010.
